%
% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\long\def\red#1{\textcolor{red}{#1}}

% Rights management information.
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2018}
\acmYear{2018}
\setcopyright{acmlicensed}
\acmConference[LA WEB]{Woodstock '18: ACM Symposium on Neural Gaze Detection}{June 03--05, 2018}{Woodstock, NY}
\acmBooktitle{Woodstock '18: ACM Symposium on Neural Gaze Detection, June 03--05, 2018, Woodstock, NY}
\acmPrice{15.00}
\acmDOI{10.1145/1122445.1122456}
\acmISBN{978-1-4503-9999-9/18/06}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID.
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{After Brazil's Data Protection Law: Authorizing Personal Data By Software Design}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
\author{Jefferson O. Silva}
\email{silvajo@pucsp.br}
\affiliation{%
  \institution{Pontifical Catholic University of S\~ao Paulo}
  \city{S\~ao Paulo}
  \country{Brazil}
}

\author{Newton Calegari}
\email{newton@nic.br}
\affiliation{%
  \institution{Brazilian Network Information Center - NIC.br}
  \city{S\~ao Paulo}
  \country{Brazil}
}

\author{Diogo Cortiz}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{S\~ao Paulo}
  \country{Brazil}
}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Silva et al.}

%
% The abstract is a short summary of the work to be presented in the article.
\begin{abstract}
Write the abstract here.

\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{Solid, Access control, Decentralized web, Frameworks, Guardian}

%
% This command processes the author and affiliation and title information and builds
% the first part of the formatted document.
\maketitle

\section{Introduction}

With the approval of the Brazilian General Data Protection Law (LGPD),\footnote{http://www.planalto.gov.br/ccivil\_03/\_Ato2015-2018/2018/Lei/L13709.htm} several software companies need to redesign the way they handle the personal data of Brazilian citizens. LGPD is based on the General Data Protection Regulation (GDPR),\footnote{http://data.consilium.europa.eu/doc/document/ST-9565-2015-INIT/en/pdf} which aims at protecting the personal data of EU individuals. In total, around 120 countries adopt comprehensive privacy laws and regulations to protect personal data held by private and public bodies \cite{Banisar2011}. Nevertheless, for the LGPD success, there must be not only fair regulation enforcement but also technological advancements, which potentially includes adopting new software development tools.


Tim Berners-Lee and colleagues propose a platform named Solid (derived from "\textbf{So}cial \textbf{li}nked \textbf{d}ata"), which \textcolor{red}{is} can be defined as a set of principles, conventions, and tools for building decentralized Web applications [\red{REF}]. Solid is based on the principle that users should have full ownership of their personal data. Currently, applications such as the social networks Facebook and LinkedIn work as "data silos" and all the personal data created in these platforms are controlled by the application companies. In constrast, decentralized Web applications provide complete separation between users' data and the applications that create and consume this data. While users store data in Web-accessible personal online datastores (pods), applications access users data relying as much as possible in W3C standards and Semantic Web technologies [\red{REF}]. Pods are by design application-agnostic and as a result users can change the application that consume their personal data at anytime. Despite incipient, Solid's architecture may be considered in several ways a technical solution to the legal framework set by LGPD and several other data protection regulations.


Nevertheless, there are several shortcomings in Solid that still need to be addressed. A significant limitation is the use of Access Control Lists to authorize a subject (e.g., an application).


\red{Some text Here}






\section{Background}
Here goes some more text.

\subsection{Brazilian Data Protection Law}
The LGPD is strong inspired by the European GDPR. The Brazilian Bill, as the European one, defines cross-border jurisdiction, thus the Bill is applicable to any organizations processing personal data of Brazilian residents, whether it is headquartered in Brazil or not.

LGPD has also included the right of data portability, the right of access to personal data by the owner, and the right of erasure. Differently of the GDPR, which imposes 30 days for the controllers to comply with these requests, the LGPD imposes 15 days.

The Brazilian law also requires companies to nominate a Data Protection Officer (DPO) who will be in charge of monitoring the adoption of best practices for personal data protection and for reporting to the National Data Protection Authority (ANPD).

The regulation defines the concepts of personal data as "any data, isolated or aggregated to another, that may allow the identification of a nutral person or subject them to a certain behavior" [\red{REF}] (IAPP: https://iapp.org/news/a/the-new-brazilian-general-data-protection-law-a-detailed-analysis/); sensitive data refers to data that may be subject to discriminatory practices, such as political opinion, sexual life, religious belief, genetic and biometric data, and it should have additional security layers; Unless it is possible to reverse-engineering the anonimized data, the law does not apply to this kind of data.

In a technical perspective, the efforts related to the decentralization of the Web help to build systems that are privacy-friendly, respecting user's privacy and in compliance with the regulations.
\textcolor{red}{Ainda nao sei se esse paragrafo fica nessa section ou na proxima.}

\subsection{Decentralized Web}
Teste \cite{Polleres2018}

\subsection{Access Control in the Decentralized Web}

This document uses ....

\section{Guardian}


\section{Conclusion}


\section{Backup Notes}
- These laws not only aim at guaranteeing individual rights, but also at fostering economic growth by establishing rules for the adequate use of personal data.

%
% The acknowledgments section is defined using the "acks" environment (and NOT an unnumbered section). This ensures
% the proper identification of the section in the article metadata, and the consistent spelling of the heading.
\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{laweb19}


\end{document}
